ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating conclusion
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. \textcolor{blue}{Besides, it also applies MPOR, two-thread analysis, and state hashing in order to further simplify verification models and provides fewer incorrect results, compared with GKLEE, GPUVerify, and CIVL.} Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support stream interleaving and implement further techniques to reduce the number of thread interleavings, by taking into account GPU symmetry.

@@

\bibitem{pereira:2016}
Pereira, P., Albuquerque, H., Silva, I., Marques, H., Monteiro, F., Ferreira, R., and Cordeiro, L.
\newblock {\em{SMT-Based Context-Bounded Model Checking for CUDA Programs}}.
\newblock Concurrency Computat.: Pract. Exper. 2016 (to appear).

@@

>>>>

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. \textcolor{blue}{Besides, it also applies MPOR, two-thread analysis, and state hashing in order to further simplify verification models and provides fewer incorrect results, compared with GKLEE, GPUVerify, and CIVL.} Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support \textcolor{blue}{CUDA (parallel) streams and events~\cite{cuda:2012}} and implement further techniques \textcolor{blue}{(e.g., Abstract Interpretation~\cite{Rocha2017})} to reduce the number of thread interleavings, by taking into account GPU symmetry.

@@

\bibitem{pereira:2016}
Pereira, P., Albuquerque, H., Silva, I., Marques, H., Monteiro, F., Ferreira, R., and Cordeiro, L.
\newblock {\em{SMT-Based Context-Bounded Model Checking for CUDA Programs}}.
\newblock Concurrency Computat.: Pract. Exper. 2016.

@@

\bibitem{Rocha2017}
\textcolor{blue}{Rocha, W., Rocha, H., Ismail, H., Cordeiro, L., and Fischer, B.}
\newblock {\em{\textcolor{blue}{DepthK: A k-Induction Verifier Based on Invariant Inference for C Programs}}}.
\newblock \textcolor{blue}{Tools and Algorithms for the Construction and Analysis of Systems: 23rd International Conference, TACAS 2017, Held as Part of the European Joint Conferences on Theory and Practice of Software, ETAPS 2017, Uppsala, Sweden.}
\newblock \textcolor{blue}{{Springer Berlin Heidelberg}, 360--364, 2017.}
